---
title: "<center> Temporal Genomics Working Group <center> "
author: "<center> Anthony Snead <center> "
date: "<center> _`r Sys.Date()`_ <center>"
output: pdf_document
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(eval = FALSE, echo=TRUE, warning=FALSE, message=FALSE)
knitr.duplicate.label = "allow"
```

```{r, Libraries}
library(tidyverse)
library(dplyr)
library(stringr)
```

# Filtering Reference List

##Import Reference List
Files were downloaded from Web of Science as text files. The below code imports the text files as a dataframe and saves the keyword used to retreive each paper as a new column by extracting it from the file name. 
```{r, Importing}

file_names <- list.files(path="C:/Users/antho/OneDrive - The University of Alabama/Temporal Genomics WKGRP/archive/", full.names = FALSE)
#getting all the files names for each text file

DB <- list.files(path="C:/Users/antho/OneDrive - The University of Alabama/Temporal Genomics WKGRP/archive/", full.names = TRUE) %>% 
  #get list of csv paths
  lapply(., read_delim,delim = "\t", escape_double = FALSE, col_names = c("Publication_Type",
                                               "Authors",
                                               "Book_Authors",
                                               "Book_Editors",
                                               "Book_Group_Authors",
                                               "Author_Full_Names",
                                               "Book_Author_Full_Names",
                                               "Group_Authors",
                                               "Article_Title",
                                               "Source_Title",
                                               "Book_Series_Title",
                                               "Book_Series_Subtitle",
                                               "Language",
                                               "Document_Type",
                                               "Conference_Title",
                                               "Conference_Date",
                                               "Conference_Location",
                                               "Conference_Sponsor",
                                               "Conference_Host",
                                               "Author_Keywords",
                                               "Keywords_Plus",
                                               "Abstract",
                                               "Addresses",
                                               "Reprint_Addresses",
                                               "Email_Addresses",
                                               "Researcher_Ids",
                                               "ORCIDs",
                                               "Funding_Orgs",
                                               "Funding_Text",
                                               "Cited_References",
                                               "Cited_Reference_Count",
                                               "Times_Cited_WoS_Core",
                                               "Times_Cited_All_Databases",
                                               "180_Day_Usage_Count",
                                               "Since_2013_Usage_Count",
                                               "Publisher",
                                               "Publisher_City",
                                               "Publisher_Address",
                                               "ISSN",
                                               "eISSN",
                                               "ISBN",
                                               "Journal_Abbreviation",
                                               "Journal_ISO_Abbreviation",
                                               "Publication_Date",
                                               "Publication_Year",
                                               "Volume",
                                               "Issue",
                                               "Part_Number",
                                               "Supplement",
                                               "Special_Issue",
                                               "Meeting_Abstract",
                                               "Start_Page",
                                               "End_Page",
                                               "Article_Number",
                                               "DOI",
                                               "Book_DOI",
                                               "Early_Access_Date",
                                               "Number_of_Pages",
                                               "WoS_Categories",
                                               "Research_Areas",
                                               "IDS_Number",
                                               "Unique_WOS_ID",
                                               "Pubmed_Id",
                                               "Open_Access_Designations",
                                               "Highly_Cited_Status",
                                               "Hot_Paper_Status",
                                               "Date_of_Export"),
         col_types = cols(Publication_Type = col_character(),
                                               Authors = col_character(),
                                               Book_Authors  = col_character(),
                                               Book_Editors  = col_character(),
                                               Book_Group_Authors = col_character(),
                                               Author_Full_Names = col_character(),
                                               Book_Author_Full_Names = col_character(),
                                               Group_Authors = col_character(),
                                               Article_Title = col_character(),
                                               Source_Title = col_character(),
                                               Book_Series_Title = col_character(),
                                               Book_Series_Subtitle = col_character(),
                                               Language = col_character(),
                                               Document_Type = col_character(),
                                               Conference_Title = col_character(),
                                               Conference_Date = col_character(),
                                               Conference_Location = col_character(),
                                               Conference_Sponsor = col_character(),
                                               Conference_Host = col_character(),
                                               Author_Keywords = col_character(),
                                               Keywords_Plus = col_character(),
                                               Abstract = col_character(),
                                               Addresses = col_character(),
                                               Reprint_Addresses = col_character(),
                                               Email_Addresses  = col_character(),
                                               Researcher_Ids  = col_character(),
                                               ORCIDs  = col_character(),
                                               Funding_Orgs = col_character(),
                                               Funding_Text = col_character(),
                                               Cited_References = col_double(),
                                               Cited_Reference_Count = col_double(),
                                               Times_Cited_WoS_Core = col_double(),
                                               Times_Cited_All_Databases = col_double(),
                                               "180_Day_Usage_Count" = col_double(),
                                               Since_2013_Usage_Count = col_double(),
                                               Publisher = col_character(),
                                               Publisher_City = col_character(),
                                               Publisher_Address = col_character(),
                                               ISSN = col_character(),
                                               eISSN = col_character(),
                                               ISBN = col_character(),
                                               Journal_Abbreviation = col_character(),
                                               Journal_ISO_Abbreviation = col_character(),
                                               Publication_Date = col_character(),
                                               Publication_Year = col_double(),
                                               Volume = col_double(),
                                               Issue = col_double(),
                                               Part_Number = col_character(),
                                               Supplement = col_character(),
                                               Special_Issue = col_character(),
                                               Meeting_Abstract = col_character(),
                                               Start_Page = col_double(),
                                               End_Page = col_double(),
                                               Article_Number = col_double(),
                                               DOI = col_character(),
                                               Book_DOI = col_character(),
                                               Early_Access_Date = col_character(),
                                               Number_of_Pages = col_double(),
                                               WoS_Categories = col_character(),
                                               Research_Areas = col_character(),
                                               IDS_Number = col_character(),
                                               Unique_WOS_ID = col_character(),
                                               Pubmed_Id = col_character(),
                                               Open_Access_Designations = col_character(),
                                               Highly_Cited_Status = col_character(),
                                               Hot_Paper_Status = col_character(),
                                               Date_of_Export = col_character()),
    trim_ws = TRUE, skip = 1 ) 
#importing the references as a list of data frames with the files name as the element name

for(i in 1:144){
  DB[[i]]$Keyword_Search <- sub("\\_.*", "", file_names[i])
}
# get colum, of keyword used in the search from the element name
```

##Filtering the Reference List

We first bind all the list elements together and get rid of duplicate articles. We then filter by various components to try and meet the filtering guidelines established in the review paper. Not all papers that are not applicable are fitlered out. Therefore, we still did a manual filtering by reading the title and abstract of each paper. 

```{r, Filtering}
Filtered_Data_Base <- DB %>%
  #start wit dataset
  bind_rows %>%
  #combine
  distinct(Authors, Article_Title, .keep_all = TRUE) %>%
  #remove duplicates
  dplyr::filter(Publication_Type == "J" & Language == "English") %>%
  #filer by language and publication type
  dplyr::filter(stringr::str_detect(Research_Areas, "Evolution|Genetic|Biodiversity|Ecology|Conservation|Marine|Freshwater|Zoology|Fisheries|Entomology|Oceanography|Genomic")
                & (Document_Type == "Article"|
                     Document_Type == "Review")) %>%
  #keep if te research area has any of these words
  dplyr::filter(!stringr::str_detect(Research_Areas, ("Agriculture|Anthropology|Archaeology|Sociology|Psychology|Microbiology|Plant|Veterinary|Forestry|Immunology|Oncology|Medicine|Obstetrics|Ophthalmology|Cell|Toxicology|Mycology|Psychiatry|Anatomy|Chemistry|physics|Paleontology|Physiology|Endocrinology|Engineering|Neurosciences|Reproductive|Energy|Cardiology|Public|Developmental| Virology"))
                & !stringr::str_detect(Source_Title , ("HUMAN|MEDICAL|FORENSIC|CLINICAL")) 
                & !stringr::str_detect(WoS_Categories, ("Clinical|Geosciences"))
                &!stringr::str_detect(Author_Keywords, ("paleo|Paleo|Anthropology|anthropology|medicine|Medicine|bacteria|Bacteria|virus|Virus|virology|Virology|archaeology|Archaeo|microsat|Microsat|allozy|Allozy|Diet|diet|Feeding|feeding|plant|trophic|Trophic|human|Human|Forest|forest|Domestic|domestic|agricult|Agricult"))
                & !stringr::str_detect(Article_Title, ("Domestic|domestic|homo|Homo|Neanderthal|neanderthal|Archeolo|archeolo|archaeo|Archaeo|Environmental DNA|environmental DNA|eDNA|Neolithic|neolithic|Pleisto|pleisto|Palaeo|Paleo|palaeo|paleo|medieval|Tribe|tribe|tribal|Tribal|mummy|human|Human|Cattle|cattle|Sheep|sheep|fossil|Fossil|Chloroplast|chloroplast|Plant|plant|Pre-quaternary|microb|Microb|farm|Farm|agriculture|Agriculture|Cancer|cancer|microsat|Microsat|allozym|Allozym|STR|sediment|Sediment|epigenetic|Epigenetic|methylation|Methylation"))
                &!stringr::str_detect(Keywords_Plus,("HUMAN|CATTLE|AGRICULTURE|FARM|DOMESTIC|CHLOROPLAST|DIET|BACTERIA|VIRUS"))) %>%
  #Remove entries which have these strings. I Did this by looking at the datas heet to evaluate the possible words which were used. Therefore, the word choice is not systematic but the subjects are. I just got rid of domesticated, human, microsats, allozyme,medical, plats, eDNA, microbiology, and epigenetic studies. 
  dplyr::filter(Publication_Year >= 2000 & !is.na(Publication_Year)) %>%
#filter by publication year
  dplyr::select(Article_Title, Authors, Abstract,Email_Addresses, Publication_Year, DOI, Source_Title, Keyword_Search )

```